Covariate analysis of CMC and HBCC matched RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (DLPFC with CQN normlaisation)

### 2017-08-28 code/Rmd/CMC_HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Minor bug fix

### Data preprocessing
Filter DLPFC SCZ and Control samples alone
```{r preprocess.data}
# Filter all ACC samples and Other samples
COVARIATES = COVARIATES %>%
  dplyr::filter(Dx.Tissue %in% c("SCZ_DLPFC", "Control_DLPFC"))

@@

ggpubr::ggarrange(plotlist = p, ncol = 4, nrow = 2)
```

@@

### Explore metatdata
```{r data.explore, fig.width = 12, fig.height = 12}
my.theme <- theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1), plot.title=element_text(hjust=0.5))

@@

ggpubr::ggarrange(plotlist = p, ncol = 4, nrow = 2)
```
### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Also remove genes with missing gene length and percentage GC content
```{r cpmnormalisation}
COUNT[is.na(COUNT)] = 0
genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Dx.Tissue), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)

>>>>

### Data preprocessing
Filter DLPFC SCZ and Control samples alone
```{r preprocess.data, fig.height=10, fig.width=15}
# Filter all ACC samples and Other samples
COVARIATES = COVARIATES %>%
  dplyr::filter(Dx.Tissue %in% c("SCZ_DLPFC", "Control_DLPFC"))

@@

p = ggpubr::ggarrange(plotlist = p, ncol = 4, nrow = 2) 
p
```

@@

### Explore metatdata
```{r data.explore, fig.width = 15, fig.height = 10}
my.theme <- theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1), plot.title=element_text(hjust=0.5))

@@

p = ggpubr::ggarrange(plotlist = p, ncol = 4, nrow = 2)
p
```
### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Also remove genes with missing gene length and percentage GC content
```{r cpmnormalisation}
COUNT[is.na(COUNT)] = 0
genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Dx.Tissue), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)
